Preliminary Thesis Defence

### 2014-01-02 south-africa.tex
add intro etc.

Our finding is that policy change had a negative effect on long-term growth metrics of young children
and the general mens pension income had a negative effect on young children's BMI.
\pagebreak

@@

@@

The anthropometrics are useful for computing z-scores.
These z-scores are considered a good representation of short-term or long-term health issues, respectively.
This relation is especially well observed for children between 6 and 60 months old.
We therefore stay with the best practice and only include those observations in our analysis.

@@

Children's anthropometrics are taken, these are length/height, weight, and waist.
Using these anthropometics and WHO growth standards, z-scores are calculated.

\subsection{WHO: Child Growth Standards}
In 2006 the WHO published its standards for child growth \parencite{who2006child}.
These standards measure the difference between a child's anthropometrics
standardised against an ideal score.

>>>>

Our finding is that policy change had a negative effect on long-term growth metrics of young children
and the general male pension income had a negative effect on young children's BMI.
\pagebreak

@@

As mentioned above, we follow \textcite{duflo2000child,duflo2003grandmothers} general design.
Looking at the gender of pension recipients gives a relatively clean analysis,
because of it's relative exogeneity.
We therefore use these as the Right-Hand Side variables, or explanata.
Anthopometrics for children are used, since these capture well, the effects of both malnutrition and disease,
the two most common health issues that we are addressing.

@@

The anthropometrics are useful for computing z-scores.
With z-scores we refer to the practice of standardising the anthropometrics using an `idea' standard \parencite{who2006child}.

For example, if we measure a height $x$ for a child of age $y$ (in weeks/months),
then we refer the to WHO tables, find the relevant ideal height and standard deviation for a child of age $y$.
We then substract the ideal height ($\mu_y$) from the observed height,
and divide by the standard devation ($\sigma_y$), like so:
\[
z_{xy} = \frac{x - \mu_y}{\sigma_{y}}
\]
We distinquish between Age Based Z-scores (ABZ) and Height-Based Z-scores (HBZ).
This is described in futher detail in \autoref{sa:data:who}.

These z-scores are considered a good representation of short-term or long-term health issues, respectively.
This relation is especially well observed for children between 6 and 60 months old.
We therefore stay with the best practice and only include those observations in our analysis.

@@

The income from the pension system is just above 1000 SAR.
There are a number of different exact amount, which we have simplified to a dummy.
Since the variation in the amount is around 5\% this should not be without much loss of generality.
\autoref{sa:ta:income} gives a description of the distribution of income as found in the NIDS data sets.

\begin{table}[hb!]
\centering
\caption{NIDS Income distribution}
\label{sa:ta:income}
\begin{tabular}{l|r}
\hline
  Min. & 0 \\
  1st Qu. & 1,070 \\
  Median & 1,870 \\
  Mean & 3,939 \\
  3rd Qu. & 3,150 \\
  Max. & 3,413,000 \\
\end{tabular}
\end{table}

Children's anthropometrics are taken, these are length/height, weight, and waist.
Using these anthropometics and WHO growth standards, z-scores are calculated.
The following z-scores are included:

\subsection{WHO: Child Growth Standards}
\label{sa:data:who}
In 2006 the WHO published its standards for child growth \parencite{who2006child}.
These standards measure the difference between a child's anthropometrics
standardised against an ideal score.
